How does increasing $s$ and $k$ effect log normalising constant estimation

### 2023-04-13 src/naomi-simple_increase-s-k/increase-s-k.Rmd
Correct typo #22

```{r}
df <- data.frame(
  s = rep(1:5, times = 3),
  k = rep(c(2, 3, 5), each = 5),
  lognormconst = c(k2_lognormconsts, k3_lognormconsts, k5_lognormconsts),
  time = c(k2_times, k3_times, k5_times),
)

>>>>

```{r}
df <- data.frame(
  s = rep(1:5, times = 3),
  k = rep(c(2, 3, 5), each = 5),
  lognormconst = c(k2_lognormconsts, k3_lognormconsts, k5_lognormconsts),
  time = c(k2_times, k3_times, k5_times)
)
